---
output:
  html_document
---


<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}

# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})


```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================

# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )

# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors

MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}

# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 

  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color

# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)

# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order

MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}



# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

# Use in ggplot 
  # scale_color_MountSinai("main")

```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y)) # Does not include
not_all_na <- function(x) all(!is.na(x)) # Exclude columns with All NAs

```


```{r Processed Data Saving Directory, echo = FALSE, warning = FALSE, message = FALSE}

path <- "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/physician-access/"

date_start <- as.Date("2022-11-01", format="%Y-%m-%d")
date_end <- as.Date("2023-01-31", format="%Y-%m-%d")

```


```{r Import Scheduling Data, echo = FALSE, warning = FALSE, message = FALSE}

scheduling_data_raw <- as.data.frame(readRDS("historical_data.rds")) %>%
  mutate(Campus = ifelse(Campus == "MSDD", "MSDMG", Campus)) %>%
  filter(!is.na(Campus)) %>%
  filter(Campus %in% c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDMG")) 


scheduling_data_raw <- scheduling_data_raw %>%
  mutate(New.PT2 = case_when(New.PT2 == "New" ~ 'New',TRUE ~ 'Established'),
         Appt.Made.DateYear = as.Date(Appt.Made.DTTM, format="%Y-%m-%d"),
         Appt.Made.MonthYear = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y-%m"),
         Appt.Made.Year = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y"),
         Appt.Cancel.DateYear = as.Date(Appt.Cancel.DTTM, format="%Y-%m-%d")) %>%
  mutate(Appt.Status = case_when(Appt.Status == "Canceled" & Appt.DateYear == Appt.Cancel.DateYear ~ "Same-Day Canceled",
                                 TRUE ~ Appt.Status)) %>%
  mutate(Visit.Method = ifelse(str_detect(Visit.Method, "PERSON"),"inPerson","telehealth"))



```


```{r Access Prioritization Specialty Mapping, echo = FALSE, warning = FALSE, message = FALSE}

amb_access_mapping <- read.csv("ambulatory_access_mapping_2.6.2023.csv")

scheduling_data_raw$specialty_access_group <- amb_access_mapping$Campus.Specialty.Group.Access[match(scheduling_data_raw$Department, amb_access_mapping$DEPARTMENT_OLD)]

```


```{r Wait Time Metrics, echo = FALSE, warning = FALSE, message = FALSE}

# Access by Specialty ----------------------------------------------------------
waitTime_specialty_access <- scheduling_data_raw %>%
  filter(Wait.Time >= 0) %>%
  # filter(Appt.Made.Year == 2022) %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  group_by(specialty_access_group) %>%
  summarise(med_wait = as.numeric(median(Wait.Time, na.rm = TRUE)))


# Access by Specialty and Access----------------------------------------------------------
waitTime_specialty_site_access <- scheduling_data_raw %>%
  filter(Wait.Time >= 0) %>%
  # filter(Appt.Made.Year == 2022) %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  group_by(specialty_access_group, Campus) %>%
  summarise(med_wait = as.numeric(median(Wait.Time, na.rm = TRUE)))

```


```{r New Patient Metrics, echo = FALSE, warning = FALSE, message = FALSE}

# Percent of New Patients Scheduled within 14 Days by Specialty -----------------
newPT_specialty_access <- scheduling_data_raw %>%
  filter(Wait.Time >= 0) %>%
  # filter(Appt.Made.Year == 2022) %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  mutate(waitTime_14days = case_when(Wait.Time <= 14 ~ "Yes",
                                    TRUE ~ "No")) %>%
  group_by(specialty_access_group, waitTime_14days) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = waitTime_14days,
              values_from = total,
              values_fill = 0) %>%
  mutate(perc_14days = Yes/(Yes+No))


# Percent of New Patients Scheduled within 14 Days by Specialty and site -----------------
newPT_specialty_site_access <- scheduling_data_raw %>%
  filter(Wait.Time >= 0) %>%
  # filter(Appt.Made.Year == 2022) %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  mutate(waitTime_14days = case_when(Wait.Time <= 14 ~ "Yes",
                                    TRUE ~ "No")) %>%
  group_by(specialty_access_group, Campus, waitTime_14days) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = waitTime_14days,
              values_from = total,
              values_fill = 0) %>%
  mutate(perc_14days = Yes/(Yes+No))

```


```{r Volume Metrics, echo = FALSE, warning = FALSE, message = FALSE}


# Volume by Specialty -----------------------------------------------------------
volume_specialty_access <- scheduling_data_raw %>%
  filter(Appt.Status == "Arrived") %>%
  # filter(Appt.Year == 2022) %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, New.PT2) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = New.PT2,
              values_from = total,
              values_fill = 0) %>%
  mutate(total = New + Established,
         new_perc = New/(total))


# Volume by Specialty and Site -----------------------------------------------------------
volume_specialty_site_access <- scheduling_data_raw %>%
  filter(Appt.Status == "Arrived") %>%
  # filter(Appt.Year == 2022) %>%
 filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, Campus, New.PT2) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = New.PT2,
              values_from = total,
              values_fill = 0) %>%
  mutate(total = New + Established,
         new_perc = New/(total))
```


```{r No Show Metrics, echo = FALSE, warning = FALSE, message = FALSE}

# Volume by Specialty -----------------------------------------------------------
noShows_specialty_access <- scheduling_data_raw %>%
  # filter(Appt.Year == 2022) %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, Appt.Status) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Appt.Status,
              values_from = total,
              values_fill = 0) 
noShows_specialty_access$total <- rowSums(noShows_specialty_access[,2:length(noShows_specialty_access)])
noShows_specialty_access <- noShows_specialty_access %>%
  mutate(noShow_perc = (`No Show` + `Same-Day Canceled`)/total)


# Volume by Specialty and Site -----------------------------------------------------------
noShows_specialty_site_access <- scheduling_data_raw %>%
  # filter(Appt.Year == 2022) %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, Campus, Appt.Status) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Appt.Status,
              values_from = total,
              values_fill = 0) 
noShows_specialty_site_access$total <- rowSums(noShows_specialty_site_access[,3:length(noShows_specialty_site_access)])
noShows_specialty_site_access <- noShows_specialty_site_access %>%
  mutate(noShow_perc = (`No Show` + `Same-Day Canceled`)/total)

```


```{r Telehealth Metrics, echo = FALSE, warning = FALSE, message = FALSE}

# Volume by Specialty -----------------------------------------------------------
tele_volume_specialty_access <- scheduling_data_raw %>%
  filter(Appt.Status == "Arrived") %>%
  # filter(Appt.Year == 2022) %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, Visit.Method) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Visit.Method,
              values_from = total,
              values_fill = 0) %>%
  mutate(tele_perc = telehealth/ (inPerson + telehealth))



# Volume by Specialty and Site --------------------------------------------------
tele_volume_specialty_site_access <- scheduling_data_raw %>%
  filter(Appt.Status == "Arrived") %>%
  # filter(Appt.Year == 2022) %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  group_by(specialty_access_group, Campus, Visit.Method) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Visit.Method,
              values_from = total,
              values_fill = 0) %>%
  mutate(tele_perc = telehealth/ (inPerson + telehealth))

```


```{r Merge Processed Scheduling Metrics, echo = FALSE, warning = FALSE, message = FALSE}

scheduling_metrics_specialty_access <- Reduce(function(x, y) merge(x, y, all=TRUE), list(waitTime_specialty_access, 
                                                                             newPT_specialty_access[,c("specialty_access_group","perc_14days")], 
                                                                             volume_specialty_access[,c("specialty_access_group","total","new_perc")],
                                                                             tele_volume_specialty_access[,c("specialty_access_group","tele_perc")],
                                                                             noShows_specialty_access[,c("specialty_access_group","noShow_perc")]))

scheduling_metrics_specialty_site_access <- Reduce(function(x, y) merge(x, y, all=TRUE), list(waitTime_specialty_site_access, 
                                                                             newPT_specialty_site_access[,c("specialty_access_group","Campus","perc_14days")], 
                                                                             volume_specialty_site_access[,c("specialty_access_group","Campus","total","new_perc")],
                                                                             tele_volume_specialty_site_access[,c("specialty_access_group","Campus","tele_perc")],
                                                                             noShows_specialty_site_access[,c("specialty_access_group","Campus","noShow_perc")]))




saveRDS(scheduling_metrics_specialty_access, "scheduling_metrics_specialty_access.rds")
saveRDS(scheduling_metrics_specialty_site_access, "scheduling_metrics_specialty_site_access.rds")

```


```{r Storage Clean Up, echo = FALSE, warning = FALSE, message = FALSE}

rm(scheduling_data_raw)
invisible(gc())

```


```{r Import Slot Data, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")


# Import Slot Availability Data ------------------------------------------------
slot_raw_tbl <- tbl(conn1, "Y_DM_BOOKED_FILLED_RATE")
access_raw_tbl <- tbl(conn1, "MV_DM_PATIENT_ACCESS")
availability_raw_tbl <- tbl(conn2, "V_AVAILABILITY")



slot_raw <- slot_raw_tbl %>%
    mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  # filter(SITE == "MSUS") %>%
  filter(Appt.Year >= 2022) %>%
  filter(Appt.Month %in% c(11,12,1)) %>%
  # collect() 
  filter(OUTSIDE_TEMPLATE_YN == "N") %>%
  filter(VISIT_PROV_STAFF_RESOURCE_C == 1) %>%
  group_by(DEPARTMENT_NAME, Appt.DateYear) %>%
  summarise(total_available_dur = sum(AVAIL_MINUTES, na.rm = TRUE),
            total_booked_dur = sum(BOOKED_MINUTES, na.rm = TRUE)) %>%
  collect() 

slot_raw <- slot_raw %>%
  filter(Appt.DateYear >= date_end & Appt.DateYear <= date_end) %>%
  mutate(Campus = ifelse(Campus == "MSDD", "MSDMG", Campus)) %>%
  filter(!is.na(Campus)) %>%
  filter(Campus %in% c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDMG")) 
  


slot_raw$specialty_access_group <- amb_access_mapping$Campus.Specialty.Group.Access[match(slot_raw$DEPARTMENT_NAME, amb_access_mapping$DEPARTMENT_OLD)]
slot_raw$Campus <- amb_access_mapping$CAMPUS[match(slot_raw$DEPARTMENT_NAME, amb_access_mapping$DEPARTMENT_OLD)]


# Booked Rate by Specialty -----------------------------------------------------
booked_rate_specialty_access <- slot_raw %>%
  group_by(specialty_access_group) %>%
  summarise(total_available = sum(total_available_dur),
            total_booked = sum(total_booked_dur)) %>%
  mutate(booked_rate = round(total_booked/total_available,2))

# Booked Rate by Specialty and Site -----------------------------------------------------
booked_rate_specialty_site_access <- slot_raw %>%
  group_by(specialty_access_group, Campus) %>%
  summarise(total_available = sum(total_available_dur),
            total_booked = sum(total_booked_dur)) %>%
  mutate(booked_rate = round(total_booked/total_available,2)) %>%
  filter(Campus != "")
  
  
```



```{r Merge Scheduling and Booked Rate, echo = FALSE, warning = FALSE, message = FALSE}

access_metrics_specialty <- left_join(scheduling_metrics_specialty_access, booked_rate_specialty_access)

access_metrics_specialty_site <- left_join(scheduling_metrics_specialty_site_access, booked_rate_specialty_site_access)

require(openxlsx)
df_list <- list("By Specialty" = access_metrics_specialty, "By Specialty and Site" = access_metrics_specialty_site)
write.xlsx(df_list, file = "Specialty Prioritization_Nov22Jan23.xlsx")

```

















```{r Guidehouse Data Request Slot Utilization, echo = FALSE, warning = FALSE, message = FALSE}

# booked_filled_site_dept <- slot_raw_tbl %>%
#   mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
#   mutate(Appt.Year = year(CONTACT_DATE),
#          Appt.Month = month(CONTACT_DATE)) %>%
#   filter(Appt.Year == 2022) %>%
#   filter(VISIT_PROV_STAFF_RESOURCE_C == 1) %>%
#   group_by(SITE, DEPARTMENT_SPECIALTY, DEPARTMENT_NAME, 
#            Appt.Year, Appt.Month, Appt.DateYear) %>%
#   summarise(total_available_dur = sum(AVAIL_MINUTES, na.rm = TRUE),
#             total_booked_dur = sum(BOOKED_MINUTES, na.rm = TRUE),
#             total_arrived_dur = sum(ARRIVED_MINUTES, na.rm = TRUE)) %>%
#   collect() %>%
#   mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m")) %>%
#   group_by(SITE, DEPARTMENT_SPECIALTY, DEPARTMENT_NAME, 
#            Appt.MonthYear) %>%
#   summarise(total_available_dur = sum(total_available_dur, na.rm = TRUE),
#             total_booked_dur = sum(total_booked_dur, na.rm = TRUE),
#             total_arrived_dur = sum(total_arrived_dur, na.rm = TRUE)) %>%
#   mutate(booked_rate = round(total_booked_dur/total_available_dur,2),
#          filled_rate = round(total_arrived_dur/total_available_dur,2)) 
# 
# 
# booked_filled_site_dept <- booked_filled_site_dept %>%
#   filter(SITE %in% c("MSBI","MSDD","MSH- Ambulatory Care","MSH-MSDFP","MSM","MSQ","MSUS","MSW","Network","Oncology"))
# 
# require(openxlsx)
# list_of_datasets <- list("By Site and Dept" = booked_filled_site_dept)
# write.xlsx(list_of_datasets, file = "Guidehouse Data Request - Booked and Filled - 2022.xlsx")

```


<!-- ```{r Provider Practicing Sites and Departments Scheduling Data, echo = FALSE, warning = FALSE, message = FALSE} -->

<!-- practicing_sites_depts <- slot_raw %>% -->
<!--   group_by(NPI, Appt.MonthYear, SITE, DEPARTMENT_NAME) %>% -->
<!--   summarise(practicing_sites = n()) %>% -->
<!--   group_by(NPI, Appt.MonthYear) %>% -->
<!--   summarise(practicing_sites = toString(unique(SITE)), -->
<!--             practicing_depts = toString(unique(DEPARTMENT_NAME))) %>% -->
<!--   mutate(practicing_sites = gsub("NA", "",practicing_sites)) -->

<!-- ``` -->


```{r Import Productivity Data, echo = FALSE, warning = FALSE, message = FALSE}

productivity_data <- read_excel(paste0(path,"Master Productivity file Budget Jan-Nov 22.xlsx"), sheet = "Master Prod 2022")


current_year_cols <- colnames(productivity_data[grepl("2022",colnames(productivity_data))])


current_prod_data <- productivity_data %>%
  dplyr::select(`Master Dept`, Speciality, Physician, NPI, `2022 Calculate %`, `current_year_cols`)

month_number <- as.numeric(format(as.Date(date_end, format="%Y-%m-%d"), "%m"))
month_cols <- format(seq(as.Date(date_start), as.Date(date_end), "months"), "%Y-%m")


# Monthly wRVU Data ------------------------------------------------------------
prov_wRVU_data <- current_prod_data[,1:(5+month_number)]
colnames(prov_wRVU_data) <- c("Master Dept","Specialty","Physician","NPI","2022 Calculated %", month_cols)
prov_wRVU_data <- prov_wRVU_data %>%
  pivot_longer(6:length(prov_wRVU_data),
               names_to = "Appt.MonthYear",
               values_to = "wRVUs") %>%
  add_column(`2022 Reported CFTE` = "", .after = "NPI") %>%
  mutate(NPI = as.character(NPI))

prov_wRVU_data$`2022 Reported CFTE` <- productivity_data$`2022 Reported CFTE `[match(prov_wRVU_data$NPI, productivity_data$NPI)]

# Monthly Collections Data -----------------------------------------------------
prov_collections_data <- current_prod_data %>%
  dplyr::select(`Master Dept`, Speciality, Physician, NPI, `2022 Calculate %`, colnames(current_prod_data[grepl("Collections",colnames(current_prod_data))]))
prov_collections_data  <- prov_collections_data [,1:(5+month_number)]
colnames(prov_collections_data) <- c("Master Dept","Specialty","Physician","NPI","2022 Calculated %",month_cols)
prov_collections_data <- prov_collections_data %>%
  pivot_longer(6:length(prov_collections_data),
               names_to = "Appt.MonthYear",
               values_to = "collections") %>%
  mutate(NPI = as.character(NPI))

```


```{r Total Template Hours, echo = FALSE, warning = FALSE, message = FALSE}

# Total Available Hours -----------------------------------------------
## Sum of Slot Length; excludes overbooking slots (only counted as one unique slot)
## Excludes Unavailable & Held Times

slot_template_hours_summary <- slot_raw_tbl %>%
  mutate(unavail = paste0(TIME_UNAVAIL_YN,DAY_UNAVAIL_YN,DAY_HELD_YN,TIME_HELD_YN)) %>%
  filter(unavail == "NNNN") %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  filter(Appt.Year == 2022) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.Year, Appt.Month, Appt.DateYear) %>%
  summarise(total_template_dur = sum(SLOT_LENGTH, na.rm = TRUE)) %>%
  collect() %>%
  mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m"),
         Appt.MonNum = as.numeric(format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%m")),
         Appt.Month = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%b"),
         Appt.Quarter = quarters(as.Date(Appt.DateYear, format="%Y-%m-%d")),
         Appt.Week = floor_date(as.Date(Appt.DateYear, format="%Y-%m-%d"), unit="week", week_start = 1),
         Appt.Day = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%a")) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, Appt.Week) %>%
  summarise(total_template_dur = sum(total_template_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear) %>%
  summarise(total_month_template_dur = sum(total_template_dur)/60,
            total_month_template_session = total_month_template_dur/4,
            avg_week_template_dur = mean(total_template_dur)/60,
            avg_week_template_session = avg_week_template_dur/(4))


saveRDS(slot_template_hours_summary, paste0(path,"slot_template_hours_summary.rds"))



slot_template_hours_summary_site <- slot_raw_tbl %>%
  mutate(unavail = paste0(TIME_UNAVAIL_YN,DAY_UNAVAIL_YN,DAY_HELD_YN,TIME_HELD_YN)) %>%
  filter(unavail == "NNNN") %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  filter(Appt.Year == 2022) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.Year, Appt.Month, Appt.DateYear) %>%
  summarise(total_template_dur = sum(SLOT_LENGTH, na.rm = TRUE)) %>%
  collect() %>%
  mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m"),
         Appt.MonNum = as.numeric(format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%m")),
         Appt.Month = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%b"),
         Appt.Quarter = quarters(as.Date(Appt.DateYear, format="%Y-%m-%d")),
         Appt.Week = floor_date(as.Date(Appt.DateYear, format="%Y-%m-%d"), unit="week", week_start = 1),
         Appt.Day = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%a")) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear, Appt.Week) %>%
  summarise(total_template_dur = sum(total_template_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear) %>%
  summarise(total_month_template_dur = sum(total_template_dur)/60,
            total_month_template_session = total_month_template_dur/4,
            avg_week_template_dur = mean(total_template_dur)/60,
            avg_week_template_session = avg_week_template_dur/(4))


saveRDS(slot_template_hours_summary_site, paste0(path,"slot_template_hours_summary_site.rds"))

# rm(slot_template_hours_summary_site)


# Arrived Hours issue found in "slot_booked_filled_check.xlsx"
# slot_booked_filled_check <- slot_raw_tbl %>%
#   filter(PROVIDER_NAME == "KIM, RENITA SUHYUN") %>%
#   filter(CONTACT_DATE == TO_DATE("2022-11-29 00:00:00", "YYYY-MM-DD HH24:MI:SS")) %>%
#   collect()
#
#
#  write_xlsx(slot_booked_filled_check, "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/slot_booked_filled_check.xlsx")

```


```{r Total Booked Hours, echo = FALSE, warning = FALSE, message = FALSE}

# Total Booked and Arrived Hours -----------------------------------------------
slot_booked_hours_summary <- slot_raw %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, VISIT_GROUP_NUM, Appt.MonthYear, Appt.Week) %>%
  summarise(total_booked_dur = sum(total_booked_dur, na.rm = TRUE)) %>%
  mutate(VISIT_GROUP_NUM = ifelse(is.na(VISIT_GROUP_NUM), "booked_established", "booked_new")) %>%
  pivot_wider(names_from = VISIT_GROUP_NUM,
              values_from = total_booked_dur,
              values_fill = 0) %>%
  mutate(booked_total = booked_established + booked_new) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear) %>%
  summarise(total_month_booked_established = sum(booked_established)/60,
            total_month_booked_new = sum(booked_new)/60,
            total_month_booked = sum(booked_total)/60,
            total_month_booked_session = total_month_booked/4,
            avg_week_booked = mean(booked_total)/60,
            avg_week_booked_session = avg_week_booked/4)

slot_booked_hours_summary <- slot_booked_hours_summary %>%
  mutate(total_month_booked_new_perc = total_month_booked_new/(total_month_booked))


saveRDS(slot_booked_hours_summary, paste0(path,"slot_booked_hours_summary.rds"))


# Total Booked and Arrived Hours -----------------------------------------------
slot_booked_hours_summary_site <- slot_raw %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, VISIT_GROUP_NUM, Appt.MonthYear, Appt.Week) %>%
  summarise(total_booked_dur = sum(total_booked_dur, na.rm = TRUE)) %>%
  mutate(VISIT_GROUP_NUM = ifelse(is.na(VISIT_GROUP_NUM), "booked_established", "booked_new")) %>%
  pivot_wider(names_from = VISIT_GROUP_NUM,
              values_from = total_booked_dur,
              values_fill = 0) %>%
  mutate(booked_total = booked_established + booked_new) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear) %>%
  summarise(total_month_booked_established = sum(booked_established)/60,
            total_month_booked_new = sum(booked_new)/60,
            total_month_booked = sum(booked_total)/60,
            total_month_booked_session = total_month_booked/4,
            avg_week_booked = mean(booked_total)/60,
            avg_week_booked_session = avg_week_booked/4)

slot_booked_hours_summary_site <- slot_booked_hours_summary_site %>%
  mutate(total_month_booked_new_perc = total_month_booked_new/(total_month_booked))


saveRDS(slot_booked_hours_summary_site, paste0(path,"slot_booked_hours_summary_site.rds"))

# Arrived Hours issue found in "slot_booked_filled_check.xlsx"
# slot_booked_filled_check <- slot_raw_tbl %>%
#   filter(PROVIDER_NAME == "KIM, RENITA SUHYUN") %>%
#   filter(CONTACT_DATE == TO_DATE("2022-11-29 00:00:00", "YYYY-MM-DD HH24:MI:SS")) %>%
#   collect()
#
#
#  write_xlsx(slot_booked_filled_check, "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/slot_booked_filled_check.xlsx")

```


```{r Total Arrived Hours, echo = FALSE, warning = FALSE, message = FALSE}


# test <- slot_raw_tbl %>%
#   filter(PROVIDER_NAME == "RAMASWAMY, RAVISHANKAR") %>%
#   collect()
# 
# write_xlsx(test, "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/arrived_hours_validation.xlsx")

# Total Arrived Hours by Provider -----------------------------------------------
slot_arrived_hours_summary <- slot_raw %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, VISIT_GROUP_NUM, Appt.MonthYear, Appt.Week) %>%
  summarise(total_arrived_dur = sum(total_arrived_dur, na.rm = TRUE)) %>%
  mutate(VISIT_GROUP_NUM = ifelse(is.na(VISIT_GROUP_NUM), "arrived_established", "arrived_new")) %>%
  pivot_wider(names_from = VISIT_GROUP_NUM,
              values_from = total_arrived_dur,
              values_fill = 0) %>%
  mutate(arrived_total = arrived_established + arrived_new) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear) %>%
  summarise(total_month_arrived_established = sum(arrived_established)/60,
            total_month_arrived_new = sum(arrived_new)/60,
            total_month_arrived = sum(arrived_total)/60,
            total_month_arrived_session = total_month_arrived/4,
            avg_week_arrived = mean(arrived_total)/60,
            avg_week_arrived_session = avg_week_arrived/4)

slot_arrived_hours_summary <- slot_arrived_hours_summary %>%
  mutate(total_month_arrived_new_perc = total_month_arrived_new/(total_month_arrived))


saveRDS(slot_arrived_hours_summary, paste0(path,"slot_arrived_hours_summary.rds"))


# Total Arrived Hours by Site -----------------------------------------------
slot_arrived_hours_summary_site <- slot_raw %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, VISIT_GROUP_NUM, Appt.MonthYear, Appt.Week) %>%
  summarise(total_arrived_dur = sum(total_arrived_dur, na.rm = TRUE)) %>%
  mutate(VISIT_GROUP_NUM = ifelse(is.na(VISIT_GROUP_NUM), "arrived_established", "arrived_new")) %>%
  pivot_wider(names_from = VISIT_GROUP_NUM,
              values_from = total_arrived_dur,
              values_fill = 0) %>%
  mutate(arrived_total = arrived_established + arrived_new) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear) %>%
  summarise(total_month_arrived_established = sum(arrived_established)/60,
            total_month_arrived_new = sum(arrived_new)/60,
            total_month_arrived = sum(arrived_total)/60,
            total_month_arrived_session = total_month_arrived/4,
            avg_week_arrived = mean(arrived_total)/60,
            avg_week_arrived_session = avg_week_arrived/4)

slot_arrived_hours_summary_site <- slot_arrived_hours_summary_site %>%
  mutate(total_month_arrived_new_perc = total_month_arrived_new/(total_month_arrived))


saveRDS(slot_arrived_hours_summary_site, paste0(path,"slot_arrived_hours_summary_site.rds"))

# Arrived Hours issue found in "slot_booked_filled_check.xlsx"
# slot_booked_filled_check <- slot_raw_tbl %>%
#   filter(PROVIDER_NAME == "KIM, RENITA SUHYUN") %>%
#   filter(CONTACT_DATE == TO_DATE("2022-11-29 00:00:00", "YYYY-MM-DD HH24:MI:SS")) %>%
#   collect()
#
#
#  write_xlsx(slot_booked_filled_check, "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/slot_booked_filled_check.xlsx")

```


```{r Unavailable Slot Reason Category Mapping, echo = FALSE, warning = FALSE, message = FALSE}

unavail_reason_mapping <- data.frame(
  unavail_reason_category = c(
    rep("TIME_UNAVAIL_RSN_C",21),
    rep("DAY_UNAVAIL_RSN_C",21),
    rep("TIME_HELD_RSN_C",3),
    rep("DAY_HELD_RSN_C",3)
  ),
  RSN_C = c(
    seq(1:21),
    seq(1:21),
    c(1, 101, 102),
    c(1, 101, 102)
  ),
  unavail_reason = c(
    rep(c("Vacation",
          "Meeting",
          "Sick",
          "Holiday",
          "Rounds",
          "Emergency",
          "Chart Review",
          "Seminar",
          "Continuing Education",
          "Delivery",
          "Surgery",
          "Equipment Repair/Maintenance",
          "Personal",
          "Attending/Precepting",
          "Other",
          "Admin",
          "Drug Reps",
          "Legal",
          "Lunch",
          "Offsite Care",
          "Provider Requested"
          ), 2),
    rep(c("Wait List", "Possible Vacation", "Provider Requested"), 2)

  )
)

unavail_reason_mapping <- unavail_reason_mapping %>%
  mutate(RSN_C = as.character(RSN_C))

```


```{r Total Unavailable Time, echo = FALSE, warning = FALSE, message = FALSE}

# Total Unavailable Time within Templates --------------------------------------
slot_unavail <- slot_raw_tbl %>%
  mutate(unavail = paste0(TIME_UNAVAIL_YN,DAY_UNAVAIL_YN,DAY_HELD_YN,TIME_HELD_YN)) %>%
  # filter(unavail %in% c("YNNN","YNNY", "NNNY")) %>%
  filter(unavail != "NNNN") %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  filter(Appt.Year == 2022) %>%
  mutate(unavail_reason_category = case_when(!is.na(DAY_UNAVAIL_RSN_C) ~ "DAY_UNAVAIL_RSN_C",
                                             !is.na(DAY_HELD_RSN_C) ~ "DAY_HELD_RSN_C",
                                             !is.na(TIME_UNAVAIL_RSN_C) ~ "TIME_UNAVAIL_RSN_C",
                                             TRUE ~ "TIME_HELD_RSN_C"),
         RSN_C = case_when(!is.na(DAY_UNAVAIL_RSN_C) ~ DAY_UNAVAIL_RSN_C,
                                             !is.na(DAY_HELD_RSN_C) ~ DAY_HELD_RSN_C,
                                             !is.na(TIME_UNAVAIL_RSN_C) ~ TIME_UNAVAIL_RSN_C,
                                             TRUE ~ TIME_HELD_RSN_C)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.Year, Appt.Month, Appt.DateYear,
           unavail_reason_category, RSN_C) %>%
  summarise(total_unavail_dur = sum(SLOT_LENGTH, na.rm = TRUE)) %>%
  collect() %>%
  mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m"),
         Appt.MonNum = as.numeric(format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%m")),
         Appt.Month = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%b"),
         Appt.Quarter = quarters(as.Date(Appt.DateYear, format="%Y-%m-%d")),
         Appt.Week = floor_date(as.Date(Appt.DateYear, format="%Y-%m-%d"), unit="week", week_start = 1),
         Appt.Day = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%a"))


slot_unavail <- slot_unavail %>%
  mutate(RSN_C = as.character(RSN_C)) %>%
  mutate(unavail_type = case_when(str_detect(unavail_reason_category, "UNAVAIL") ~ "Unavailable",
                                  TRUE ~ "Held"))


slot_unavail <- left_join(slot_unavail, unavail_reason_mapping, by = c("unavail_reason_category","RSN_C"))

saveRDS(slot_unavail, paste0(path,"physician-access/slot_unavail.rds"))


# Total Time Unavailable -------------------------------------------------------
slot_unavail_day_summary <- slot_unavail %>%
  filter(unavail_reason_category == "DAY_UNAVAIL_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_unavail_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_unavail_day_dur = sum(total_unavail_dur)/60,
            total_month_unavail_day_session = total_month_unavail_day_dur/4,
            avg_week_unavail_day_dur = mean(total_unavail_dur)/60,
            avg_week_unavail_day_session = avg_week_unavail_day_dur/(4))

slot_unavail_time_summary <- slot_unavail %>%
  filter(unavail_reason_category == "TIME_UNAVAIL_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_unavail_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_unavail_time_dur = sum(total_unavail_dur)/60,
            total_month_unavail_time_session = total_month_unavail_time_dur/4,
            avg_week_unavail_time_dur = mean(total_unavail_dur)/60,
            avg_week_unavail_time_session = avg_week_unavail_time_dur/(4))


# Total Time Held --------------------------------------------------------------
slot_held_day_summary <- slot_unavail %>%
  filter(unavail_reason_category == "DAY_HELD_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_held_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_held_day_dur = sum(total_held_dur)/60,
            total_month_held_day_session = total_month_held_day_dur/4,
            avg_week_held_day_dur = mean(total_held_dur)/60,
            avg_week_held_day_session = avg_week_held_day_dur/(4))

slot_held_time_summary <- slot_unavail %>%
  filter(unavail_reason_category == "TIME_HELD_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_held_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_held_time_dur = sum(total_held_dur)/60,
            total_month_held_time_session = total_month_held_time_dur/4,
            avg_week_held_time_dur = mean(total_held_dur)/60,
            avg_week_held_time_session = avg_week_held_time_dur/(4))



saveRDS(slot_unavail_day_summary, paste0(path,"slot_unavail_day_summary.rds"))
saveRDS(slot_unavail_time_summary, paste0(path,"slot_unavail_time_summary.rds"))

saveRDS(slot_held_day_summary, paste0(path,"slot_held_day_summary.rds"))
saveRDS(slot_held_time_summary, paste0(path,"slot_held_time_summary.rds"))


# By Site ----------------------------------------------------------------------
# Total Unavailable Time within Templates --------------------------------------
slot_unavail_site <- slot_raw_tbl %>%
  mutate(unavail = paste0(TIME_UNAVAIL_YN,DAY_UNAVAIL_YN,DAY_HELD_YN,TIME_HELD_YN)) %>%
  # filter(unavail %in% c("YNNN","YNNY", "NNNY")) %>%
  filter(unavail != "NNNN") %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  filter(Appt.Year == 2022) %>%
  mutate(unavail_reason_category = case_when(!is.na(DAY_UNAVAIL_RSN_C) ~ "DAY_UNAVAIL_RSN_C",
                                             !is.na(DAY_HELD_RSN_C) ~ "DAY_HELD_RSN_C",
                                             !is.na(TIME_UNAVAIL_RSN_C) ~ "TIME_UNAVAIL_RSN_C",
                                             TRUE ~ "TIME_HELD_RSN_C"),
         RSN_C = case_when(!is.na(DAY_UNAVAIL_RSN_C) ~ DAY_UNAVAIL_RSN_C,
                                             !is.na(DAY_HELD_RSN_C) ~ DAY_HELD_RSN_C,
                                             !is.na(TIME_UNAVAIL_RSN_C) ~ TIME_UNAVAIL_RSN_C,
                                             TRUE ~ TIME_HELD_RSN_C)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.Year, Appt.Month, Appt.DateYear,
           unavail_reason_category, RSN_C) %>%
  summarise(total_unavail_dur = sum(SLOT_LENGTH, na.rm = TRUE)) %>%
  collect() %>%
  mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m"),
         Appt.MonNum = as.numeric(format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%m")),
         Appt.Month = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%b"),
         Appt.Quarter = quarters(as.Date(Appt.DateYear, format="%Y-%m-%d")),
         Appt.Week = floor_date(as.Date(Appt.DateYear, format="%Y-%m-%d"), unit="week", week_start = 1),
         Appt.Day = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%a"))


slot_unavail_site <- slot_unavail_site %>%
  mutate(RSN_C = as.character(RSN_C)) %>%
  mutate(unavail_type = case_when(str_detect(unavail_reason_category, "UNAVAIL") ~ "Unavailable",
                                  TRUE ~ "Held"))


slot_unavail_site <- left_join(slot_unavail_site, unavail_reason_mapping, by = c("unavail_reason_category","RSN_C"))


# Total Time Unavailable -------------------------------------------------------
slot_unavail_day_summary_site <- slot_unavail_site %>%
  filter(unavail_reason_category == "DAY_UNAVAIL_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_unavail_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_unavail_day_dur = sum(total_unavail_dur)/60,
            total_month_unavail_day_session = total_month_unavail_day_dur/4)

slot_unavail_time_summary_site <- slot_unavail_site %>%
  filter(unavail_reason_category == "TIME_UNAVAIL_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_unavail_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_unavail_time_dur = sum(total_unavail_dur)/60,
            total_month_unavail_time_session = total_month_unavail_time_dur/4)



# Total Time Held --------------------------------------------------------------
slot_held_day_summary_site <- slot_unavail_site %>%
  filter(unavail_reason_category == "DAY_HELD_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_held_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_held_day_dur = sum(total_held_dur)/60,
            total_month_held_day_session = total_month_held_day_dur/4)

slot_held_time_summary_site <- slot_unavail_site %>%
  filter(unavail_reason_category == "TIME_HELD_RSN_C") %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, Appt.MonthYear, Appt.Week, unavail_reason_category) %>%
  summarise(total_held_dur = sum(total_unavail_dur, na.rm = TRUE)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.MonthYear, unavail_reason_category) %>%
  summarise(total_month_held_time_dur = sum(total_held_dur)/60,
            total_month_held_time_session = total_month_held_time_dur/4)


saveRDS(slot_unavail_day_summary_site, paste0(path,"slot_unavail_day_summary_site.rds"))
saveRDS(slot_unavail_time_summary_site, paste0(path,"slot_unavail_time_summary_site.rds"))

saveRDS(slot_held_day_summary_site, paste0(path,"slot_held_day_summary_site.rds"))
saveRDS(slot_held_time_summary_site, paste0(path,"slot_held_time_summary_site.rds"))


```


```{r Slot Unavailable Details, echo = FALSE, warning = FALSE, message = FALSE}

slot_unavail_detail_prov <- slot_unavail %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.Year, Appt.MonthYear, Appt.Day, Appt.DateYear, unavail_type, unavail_reason) %>%
  summarise(total_unavail_dur = sum(total_unavail_dur)) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, Appt.Year, Appt.MonthYear, Appt.Day, unavail_type, unavail_reason) %>%
  summarise(avg_day_unavail_dur = round(mean(total_unavail_dur)),
            total_unavail_dur = sum(total_unavail_dur)) 

saveRDS(slot_unavail_detail_prov, paste0(path,"slot_unavail_detail_prov.rds"))

```


```{r First and Last Slot, echo = FALSE, warning = FALSE, message = FALSE}

slot_first_last_summary_site <- slot_raw_tbl %>%
  # mutate(unavail = paste0(TIME_UNAVAIL_YN,DAY_UNAVAIL_YN,DAY_HELD_YN,TIME_HELD_YN)) %>%
  # filter(unavail == "NNNN") %>%
  filter(BOOKED_MINUTES > 0) %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE)) %>%
  mutate(Appt.Year = year(CONTACT_DATE),
         Appt.Month = month(CONTACT_DATE)) %>%
  filter(Appt.Year == 2022) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, DEPARTMENT_NAME, Appt.DateYear) %>%
  summarise(start = min(SLOT_BEGIN_TIME),
            end = max(SLOT_BEGIN_TIME),
            total_booked_dur = sum(BOOKED_MINUTES, na.rm = TRUE)) %>%
  collect() %>%
  mutate(`First Slot Time` = format(as.POSIXct(as.ITime(start, format = "%H:%M")), "%H:%M"),
         `Last Slot Time` = format(as.POSIXct(as.ITime(end, format = "%H:%M")), "%H:%M")) %>%
  mutate(Appt.MonthYear = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%Y-%m"),
         Appt.MonNum = as.numeric(format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%m")),
         Appt.Month = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%b"),
         Appt.Quarter = quarters(as.Date(Appt.DateYear, format="%Y-%m-%d")),
         Appt.Week = floor_date(as.Date(Appt.DateYear, format="%Y-%m-%d"), unit="week", week_start = 1),
         Appt.Day = format(as.Date(Appt.DateYear, format="%Y-%m-%d"), "%a")) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, DEPARTMENT_NAME, Appt.MonthYear, Appt.Day) %>%
  mutate(avg_daily_booked_dur = mean(total_booked_dur, na.rm = TRUE)/60) %>%
  group_by(NPI, VISIT_PROV_STAFF_RESOURCE_C, SITE, DEPARTMENT_NAME, Appt.MonthYear, Appt.Day, `First Slot Time`, `Last Slot Time`, avg_daily_booked_dur) %>%
  summarise(total_days = n())  %>%
  # pivot_longer(c("First Slot Time","Last Slot Time"),
  #             names_to = "slot_type",
  #             values_to = "time") %>%
  # arrange(time) %>%
  arrange(NPI, Appt.MonthYear, factor(Appt.Day, levels = c("Mon","Tue","Wed","Thu","Fri","Sat","Sun"))) 

# slot_first_last_summary_site <- slot_first_last_summary_site %>%
#   mutate(total_bookable_dur = difftime(as.POSIXct(`Last Slot Time`,format="%H:%M"), as.POSIXct(`First Slot Time`,format="%H:%M"), "mins"))

saveRDS(slot_first_last_summary_site, paste0(path,"slot_first_last_summary_site.rds"))

```


```{r Provider NPI Crosscheck, echo = FALSE, warning = FALSE, message = FALSE}

slot_data_providers <- slot_raw_tbl %>%
  group_by(NPI, PROVIDER_NAME) %>%
  summarise(total = n()) %>%
  collect() %>%
  rename(PROVIDER_NAME_SLOT_DATA = PROVIDER_NAME)

slot_data_providers$total <- NULL

access_data_providers <- scheduling_data_raw %>%
  group_by(NPI, Provider) %>%
  summarise(total = n()) %>%
  dplyr::select(-total) %>%
  rename(PROVIDER_NAME_ACCESS_DATA = Provider)


npi_provider_names_crosswalk <- merge(slot_data_providers, access_data_providers, all = TRUE)

write_xlsx(npi_provider_names_crosswalk,paste0(path, "Epic NPI Provider Name Mapping.xlsx"))

```

